
% https://www.overleaf.com/
\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=0.5cm,
    bottom=0.0cm,
    left=2cm,
    right=2cm,
    footskip=0.8cm
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Ahmed Hamada's CV},
    pdfauthor={Ahmed Hamada},
    pdfcreator={LaTeX},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
\fi

\usepackage{charter}

% General settings:
\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{0pt}{0.2cm}{0.15cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.08cm,
        parsep=0.08cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
}

\begin{document}
\renewcommand{\baselinestretch}{0.95}\selectfont

% ================ HEADER ================
\begin{center}
    {\fontsize{25pt}{15pt}\selectfont Ahmed Hamada}

    {\large \textbf{Full-Stack Developer}}

    \vspace{5pt}

    Cairo, Egypt \,|\,
    \href{mailto:contact@ahmed-hamada.dev}{contact@ahmed-hamada.dev} \,|\,
    \href{tel:+201060257232}{+20 106 025 7232} \,|\,
    \href{https://github.com/ahmed-hamada-dev}{github.com/ahmed-hamada-dev} \,|\,
    \href{https://linkedin.com/in/ahmed-hamada-dev}{linkedin.com/in/ahmed-hamada-dev} \,|\,
    \href{https://ahmed-hamada.dev}{ahmed-hamada.dev}
\end{center}

\vspace{0.15cm}

% ================ SUMMARY ================
\section{Summary}

Full-Stack Developer with 3 production platforms shipped end-to-end. Built a school management system (40+ models, 6 dashboards, real-time GPS tracking), an LMS with Apple Pay, and an education ERP — all live and serving real users. Proficient in \textbf{TypeScript, Next.js, Hono.js, PostgreSQL, Prisma}.

% ================ TECHNICAL SKILLS ================
\section{Technical Skills}

\textbf{Frontend:} TypeScript, React.js, Next.js 15, TanStack Start, TanStack Query, Tailwind CSS, Framer Motion, Shadcn UI

\vspace{0.08cm}

\textbf{Backend:} Node.js, Bun, Hono.js, Express.js, Prisma ORM, PostgreSQL, Redis, BullMQ, WebSockets, OpenAPI

\vspace{0.08cm}

\textbf{Integrations:} Firebase FCM, Google Maps API, Stripe, Moyasar (Apple Pay), Bunny Stream, Twilio, Better Auth

\vspace{0.08cm}

\textbf{DevOps \& Tools:} Git, GitHub, Docker, Coolify, Vercel

% ================ EXPERIENCE ================
\section{Experience}

\textbf{Freelance Full-Stack Developer} \hfill \textit{2025 -- Present}

\vspace{0.08cm}

\textbf{School Platform} — Backend \& Web Developer (2-person team)
\begin{highlights}
    \item Architected \textbf{40+ database models} and \textbf{100+ REST API endpoints} powering 6 role-specific dashboards (Admin, Manager, Teacher, Student, Parent, Driver) for a school management platform.
    \item Developed a \textbf{real-time GPS bus tracking system} using WebSockets and Google Maps, enabling live parent notifications, trip recording \& replay, and geo-fenced school radars.
    \item Engineered a \textbf{gamified Mental Math engine} with 5 modes including inter-school competitions with deterministic PRNG for cheat-proof grading.
    \item Designed 3 course payment flows (same-school free access, cross-school manager payments, independent teacher sales) with audit logging and trip archiving.
    \item Deployed to production on a VPS via Coolify with containerized PostgreSQL, Redis, and BullMQ workers.
    \item \textit{Stack: Hono.js, TanStack Start, Prisma, PostgreSQL, Redis, BullMQ, WebSockets, Google Maps, Firebase FCM, OpenAPI.}
\end{highlights}

\vspace{0.15cm}

\textbf{Spider Platform} — Solo Developer \hfill \href{https://fy.sa}{fy.sa}
\begin{highlights}
    \item Designed and shipped a complete \textbf{LMS} end-to-end: course builder, Bunny video streaming, Apple Pay (Moyasar), gamified quizzes, and analytics dashboard.
    \item Implemented 3 auth methods (Better Auth, Google OAuth, WhatsApp OTP via Twilio), serving active users in production.
    \item \textit{Stack: Next.js 15, TypeScript, Prisma, PostgreSQL, Better Auth, Recharts.}
\end{highlights}

\vspace{0.15cm}

\textbf{Brave Online} — Backend \& Web Developer (2-person team) \hfill \href{https://braveonline.online}{braveonline.online} \,|\, \href{https://github.com/ahmed-hamada-dev/show-cases/blob/main/braveonlin.online/brave-online-README.md}{GitHub}
\begin{highlights}
    \item Architected the full backend and admin/teacher dashboards for an education ERP supporting RBAC, 3 enrollment methods, real-time chat, and device-based security.
    \item Designed a monorepo with shared Zod schema layer, enabling end-to-end type safety across Hono.js backend and TanStack Start frontend.
    \item \textit{Stack: Hono.js, TanStack Start, Prisma, PostgreSQL, Redis, BullMQ, Firebase FCM, OpenAPI.}
\end{highlights}

\vspace{0.15cm}

\textbf{Software Engineer Trainee}, ITI — Assiut, Egypt \hfill \textit{Oct 2025 -- Present}
\begin{highlights}
    \item Enrolled in a 9-month intensive program focused on modern web technologies, software architecture, and engineering practices.
\end{highlights}


% ================ EDUCATION ================
\section{Education}

\textbf{EELU} — B.Sc. in Computer Science \hfill \textit{Oct 2021 -- June 2025} \\
Grade: Very Good with Honor

% ================ LANGUAGES ================
\section{Languages}

\textbf{Arabic:} Native \hfill
\textbf{English:} Professional Proficiency

\end{document}